Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-10-29 Draft/draft.tex
Fixing introduction.

\author[1]{Honghao Fu}

@@

\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
%\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$, ($2019$)).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generators
	are at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

It has been shown that certain quantum correlations require the distant parties to share
a particular entangled state up to some local isometry. 
This phenomenon is referred to as self-testing.  
If we can further prove that, when the observed correlation deviates 
from the ideal one to some extent, 
the shared state is close to the ideal state up to some local isometry,
then we say the self-test is robust.

Self-testing is powerful because only classical interactions are performed.
Hence, it allows a classical party to delegate quantum computations to some untrusted service provider
and verify that the computations are performed
honestly and correctly \cite{ruv2013,coladan2017verifier}.
It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
lower bounds of the computational power of entanglement-assisted
multiprover interactive proof systems \cite{fitzsimons2019, neexp}.

The case of robust self-testing of the EPR pair, 
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
is fully understood.
The techniques for this case are 
first introduced in \cite{mckague2012}, then improved in \cite{bamps2015}. 
Robust self-testing of partially entangled qubits is proved later in
\cite{yang2013}, which also proposed an generalized swap-isometry
that can be used to robustly self-test large dimensional maximally entangled states.
Robust self-testings of tensor product of maximally and partially entangled qubits 
are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
with the last one being the one with the smallest input and output alphabets.
Self-testing of all pure bipartite entangled states is proved in \cite{coladan2017all}.
The authors in \cite{coladan2017all} constructed a family of correlations such
that an entangled state of any local dimension has
a self-testing correlation in this family.
% One can also self-test many copies of the $2$-dimensional EPR
% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
% The most efficient way uses $O(\log n)$ bits question and
% answers to self-test $n$ copies of $2$-dimensional EPR
% pair \cite{lowdegree}.
% Self-testing general $d$-dimensional EPR pairs is a harder task.
% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
To generate a correlation in the family, Alice and Bob
use constant-sized input alphabets but $\Theta(d)$-sized output alphabets, 
where $d$ is the local dimension of the entangled state. 
This is the only result about self-testing the general $d$-dimensional entangled state so far.
However, proving the robustness of this family of correlations remains an open problem.

Our work aims at answering two open questions.
The first one is whether maximally entangled states with large local dimension
can be self-tested with constant-sized input and output alphabets, 
which are independent of the local dimension of the self-tested state.
For comparisons, all the correlations used in the results listed above
have either input or output alphabets with sizes dependent on the
local dimension of the entangled state.
The second one is how to robustly self-test maximally entangled states
with large local dimension and no tensor product structure. 
We give an affirmative answers to the first question and
make significant progress in answering the second question
by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

@@

To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
input and constant-sized output alphabets
for each odd prime number $d$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
the distributions in $\fC(d,r)$ do. 
Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
state of dimension $4(d-1)$, we apply it to all $d \in D$
and prove \cref{thm:inf}.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}

@@

Our linear system game is designed to enforce the relation 
\begin{align*}
    U O U\ct = O^r,
\end{align*}
for unitaries $U$ and $O$, and some integer $r$.
It implies that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
\end{align*}
This relation implies the eigenvalues of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
It also implies that $U$ is a permutation of the eigenbasis of $O$.
Winning this linear system game implies that Alice and Bob share a state
$\ket{\psi}$ such that
\begin{align*}
    O \x O \ket{\psi} = \ket{\psi}, && 
    U \x U \ket{\psi} = \ket{\psi}.
\end{align*}
These two relations are important for the self-testing argument.
The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
is spanned by tensor products of states in the eigenbasis of $O$.
The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
under the permutation induced by $U$. 
At this point, the eigenvalues of $O$ are unknown, so
certifying the eigenvalues of $O$ requires another test, 
which will be introduced later.

The special feature of our linear system game is that the sizes
of the question sets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$.
Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
game only uses constant-sized question sets and constant-sized answer sets.

@@

At this point, we have the explicit structure of $O$, so we 
can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
to prove the correlation $\fC(r, d)$ can robustly self-test 
a maximally entangled state of dimension $4(d-1)$,
\begin{align*}
    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
    \ket{EPR}^{\x 2}.
\end{align*}

In the proof, we demonstrate a new way to apply the generalized swap-isometry
proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.

@@

A quantum strategy of a nonlocal game or a nonlocal test presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_{a \in \calA_x} \}_{x \in \calX}$ on Alice's side, 
$\{\{N_y^b\}_{b \in \calB_y} \}_{y \in \calY}$ on Bob's side, and a shared state $\ket{\psi}$. 
By projective measurements, we mean that  
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
\end{align}
for each $(x,y) \in \calX \times \calY$ and $(a,b) \in \calA_x \times \calB_y$.
Note that the tensor product structure indicates that the
two parties cannot communicate with each other, 
which is the reason why we say such task is nonlocal.
For simplicity we omit the tensor product symbol between operators 
acting on different Hilbert spaces in the rest of the work. 
If $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
\calH_B \rightarrow \calH_B$, 
then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
\begin{definition}
	Given input alphabets: $\calX$ and $\calY$, and families of output
	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
\end{definition}
The size of a correlation is the sum of the sizes of the conditional probability distributions in the correlation.

@@

%---------------------------------------------------
\subsection{The game $\LS(r)$}
\label{sec:lsr_def}
%---------------------------------------------------
From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
we associate a variable $x(s)$ to each generator $s \in S$.
Then each linear relation in $R$ can be translated to a linear equation.
For example, the linear relation $f_0f_1f_2 = e$ is translated 
to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
$f_1g_1m_2 = J$ is translated to the equation
$x(f_1) + x(g_1) + x(m_2) = 1$. 
The complete list of the equations is given in \cref{def:lsg_eq}.
\begin{definition}
\label{def:lsg}
The linear system game $\LS(r)$ consists of
\begin{align*}
    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
    & \calY^{\LS} = \{ x(s) : s \in S \},
\end{align*}
where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
and $\mr := 14r + 62$ is the number of equations.  
Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
Alice answer sets are 
\begin{align*}
    \calA^{\LS}_{I_i} = (\Z_2)^{I_i}
\end{align*}
for $1 \leq i \leq \mr$.
Bob's answer set is
\begin{align*}
    \calB^{\LS} = \Z_2.
\end{align*}
The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
\begin{align*}
    \pi^{\LS}(I_i, x(s)) = 
    \begin{cases}
        1/N(r) & \text{ if } s \in I_i \\
        0 & \text{otherwise,}
    \end{cases}
\end{align*}
where $N(r) := 157r + 685$ is the total number of valid question pairs.
We define 
\begin{align*}
    X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \},
\end{align*}
which is the set of all the valid answers of equation $i$.
Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
the score function is
\begin{align*}
    V^{\LS}_{I_i, x(s)}(\ba, b) = 
    \begin{cases}
        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
        0 \text{, otherwise}.
    \end{cases}
\end{align*}
\end{definition}

The construction of $\LS(r)$ proves the following theorem.
\begin{theorem}
	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
\end{theorem}
As indicated in \cref{def:lsg}, the total
number of question pairs is $N(r) = 157r + 685 = \Theta(r)$.

@@

%====================================================
\section{Extending the weighted CHSH inequality $\I_\alpha$ into a nonlocal test}
\label{sec:ext_chsh}
%====================================================
In this section, we introduce the extended weighted CHSH test,
which is going to be a component of the full test introduced in \cref{sec:full_test}.
The ideal correlation for this test contains the ideal correlation that 
achieves $\I_{-\cot(\pi/d)}^{\max}$. 
To make the study of the implication of a strategy that realize 
the ideal correlation of the extended weighted CHSH test easier,
we fill in the background of the robust self-testing property of the
general weighted CHSH inequality, $\I_\alpha$, first.

@@

% Intuitively, robust self-testing means that if some quantum strategy achieves a value $\I_\alpha$ that is close to $\I_\alpha^{\max}$,
% then the shared state must be close to $\ket{EPR}$ and their observables are close to the rotated Pauli operators 
% defined in \cref{def:ideal},
% up to some local isometry.
The formal statement is given in the theorem below. Since the proof uses the same techniques as in \cite{bamps2015},
we defer the proof till \cref{sec:w_chsh_proof}, and we only list the key relations that will be reused in \cref{sec:main} here.
\begin{theorem}
\label{thm:selftest}
    Define $\mu := \arctan(1/\alpha)$.
	If a quantum strategy $(\ket{\psi}, \{M_x:=M_x^0-M_x^1\}_{x=1,2}, \{N_y :=N_y^0-N_y^1\}_{y = 1,2} )$ achieves that
	$\I_\alpha \geq \I_\alpha^{\max} - \epsilon$
	for some $\epsilon > 0$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{junk}$  such that
	\begin{align*}
		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{junk} \x (\tM_x \x \tN_y) \ket{EPR}^{\x 2}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
		\frac{1}{\sin(\mu)^{3/2}})) \sqrt{\epsilon}
	\end{align*}
	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $\tM_x, \tN_y$ are 
	defined in \cref{def:ideal}.  
\end{theorem}
We follow the convention used in \cite{bamps2015},
which defines
\begin{align*}
	&Z_A := M_1 && X_A := M_2\\
	&Z_B := \frac{N_1+N_2}{2\cos{\mu}} && X_B := \frac{N_1-N_2}{2\sin{\mu}}.
\end{align*}
The key relations that will be reused are
\begin{align}
% 	\label{eq:za-zb}& Z_A\ket{\psi} \appd{O( \sqrt{\mu} \se)} Z_B\ket{\psi},\\
% 	\label{eq:xa-xb}&X_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B \ket{\psi}, \\
% 	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B(\1-Z_A) \ket{\psi},\\
% 	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} Z_B(\1-X_A) \ket{\psi},\\
% 	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} -X_AZ_A \ket{\psi},\\
% 	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{O(\frac{\se}{\mu^{3/2}})} -X_BZ_B \ket{\psi},
\label{eq:za-zb}& Z_A\ket{\psi} \appd{\frac{\sqrt{s\epsilon}}{c}} Z_B\ket{\psi},\\
	\label{eq:xa-xb}&X_A\ket{\psi} \appd{\frac{\sqrt{\epsilon}}{\sqrt{s}}} X_B \ket{\psi}, \\
	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{\frac{c+1}{c\sqrt{s}} \se} X_B(\1-Z_A) \ket{\psi},\\
	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{ \frac{s+1}{c\sqrt{s}} \se} Z_B(\1-X_A) \ket{\psi},\\
	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{\frac{1+c+s}{c\sqrt{s}} \se} -X_AZ_A \ket{\psi},\\
	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{\frac{2s^2+cs+c+s}{cs\sqrt{s}} \sqrt{\epsilon}} -X_BZ_B \ket{\psi}.
\end{align}
We keep the exact error terms so that some
of the substitution steps in \cref{sec:main} are 
easier to follow.

>>>>

\author{Honghao Fu
\footnote{\href{mailto:h7fu@umd.edu}{h7fu@umd.edu}}}

@@

\date{}
\affil{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA
\break
}
%\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$, ($2019$)).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generators
	are at most $5$ (M. Murty \textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

It has been shown that certain quantum correlations require the distant parties to share
a particular entangled state up to some local isometry. 
This phenomenon is referred to as self-testing.  
If we can further prove that, when the observed correlation deviates 
from the ideal one to some extent, 
the shared state is still close to the ideal state up to some local isometry,
then we say the self-test is robust.

The fact that the verifier only interacts classically with the unknown device
makes self-testing a powerful tool 
for applications in 
quantum cryptography and computational
complexity theory.
It allows a classical party to delegate quantum computations to some untrusted service provider
and verify that the computations are performed
honestly and correctly \cite{ruv2013,coladan2017verifier}.
It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
\cite{mayersyao,vv2014,fu2018}.
Since the setting of multi-prover interactive proof systems is similar to a self-test, self-testing arguments also help to prove
lower bounds of the computational power of entanglement-assisted
multiprover interactive proof systems \cite{fitzsimons2019, neexp}.

The case of robust self-testing of the EPR pair, 
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
is fully understood.
The techniques for this case are 
first introduced in \cite{mckague2012}, then improved in \cite{bamps2015}. 
Robust self-testing of partially entangled qubits is proved later in
\cite{yang2013}, the authors of which also propose an generalized swap-isometry
that can be used to robustly self-test large dimensional maximally entangled states.
Robust self-testings of tensor product of maximally and partially entangled qubits 
are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
with the last one being the one with the smallest input and output alphabets.
Self-testing of all pure bipartite entangled states is proved in \cite{coladan2017all}.
The authors of \cite{coladan2017all} construct a family of correlations such
that an entangled state of any local dimension has
a self-testing correlation in this family.
% One can also self-test many copies of the $2$-dimensional EPR
% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
% The most efficient way uses $O(\log n)$ bits question and
% answers to self-test $n$ copies of $2$-dimensional EPR
% pair \cite{lowdegree}.
% Self-testing general $d$-dimensional EPR pairs is a harder task.
% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
To generate a correlation in the family, Alice and Bob
use constant-sized input alphabets but size-$d$ output alphabets, 
where $d$ is the local dimension of the entangled state. 
The robustness of this family of correlations is proved in \cite{inf_sep}.

Our work aims at minimizing the sizes of the input 
and output alphabets of a correlation that can self-test
a maximally entangled states with large local dimension.
% that are independent of the local dimension of the self-tested state.
For comparisons, all the correlations used in the results listed above
have either input or output alphabets with sizes dependent on the
local dimension of the entangled state.
Our progress is summarized in the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

@@

\subsection{Proof overview}

To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
input and constant-sized output alphabets
for each odd prime number $d$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that the sizes of the input or output alphabet of $\fC(d,r)$ is independent of $d$. 
% the distributions in $\fC(d,r)$ do. 
Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
state of dimension $4(d-1)$, we apply it to all $d \in D$
and prove \cref{thm:inf}.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}

@@

Our linear system game, $\LS(r)$, is designed to enforce the relation 
\begin{align}
\label{eq:uor}
    U O U\ct = O^r,
\end{align}
for unitaries $U$ and $O$, and some integer $r$.
The inspiration comes from Slofstra's seminal work \cite{slofstra2017},
where he proves that 
there exists a binary linear system game that cannot be won by 
any finite-dimensional quantum strategy but a limit of 
finite-dimensional strategies can win it perfectly.
It implies that the set of quantum correlations generated by
finite-dimensional strategies is not closed.
In the proof, he proposes and validates a new way 
to design binary linear system games to enforce conjugacy relations of the
form $X Y X\ct = Z$ for unitaries $X, Y$ and $Z$.

Following Slofstra's design, 
the game $\LS(r)$ is constructed so that the sizes
of the input alphabets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$.
Restricting $r \leq 5$ as in \cref{thm:inf} implies that 
$\LS(r)$ only uses constant-sized input and output alphabets.

The reason that we choose \cref{eq:uor} to be the relation enforced
by $\LS(r)$ is the following.
Winning $\LS(r)$ implies that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2
\end{align*}
with $U$ and $O$ satisfying \cref{eq:uor}.
Then we can deduce that the eigenvalues of $O$ must be
of the form $\omega_d^j = e^{i 2j\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
We can also deduce that $U$ is a permutation of the eigenbasis of $O$.
Winning this linear system game also implies that Alice and Bob share a state
$\ket{\psi}$ such that $\ket{\psi}$
is spanned by tensor products of states in the eigenbasis of $O$,
and is invariant under the permutation induced by $U$
% \begin{align*}
%     O \x O \ket{\psi} = \ket{\psi}, && 
%     U \x U \ket{\psi} = \ket{\psi}.
% \end{align*}
% The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
% is spanned by tensor products of states in the eigenbasis of $O$.
% The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
% under the permutation induced by $U$. 
At this point, the eigenvalues of $O$ are unknown, so
certifying the eigenvalues of $O$ requires another test.

@@

At this point, we have the explicit structure of $O$, so we 
can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
to prove the correlation $\fC(r, d)$ can robustly self-test 
a maximally entangled state of dimension $4(d-1)$,
\begin{align*}
    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
    \ket{EPR}^{\x 2}.
\end{align*}
In this proof, we demonstrate a new way to apply the generalized swap-isometry
proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
dimension.

@@

A quantum strategy of a nonlocal game or a nonlocal test presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_{a \in \calA_x} \}_{x \in \calX}$ on Alice's side, 
$\{\{N_y^b\}_{b \in \calB_y} \}_{y \in \calY}$ on Bob's side, and a shared state $\ket{\psi}$. 
By projective measurements, we mean that  
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{a,b}{x,y} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
\end{align}
for each $(x,y) \in \calX \times \calY$ and $(a,b) \in \calA_x \times \calB_y$.
Note that the tensor product structure indicates that the
two parties cannot communicate with each other, 
which is the reason why we say such task is nonlocal.
For simplicity we omit the tensor product symbol between operators 
acting on different Hilbert spaces in the rest of the work. 
If $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
\calH_B \rightarrow \calH_B$, 
then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
\begin{definition}
	Given input alphabets: $\calX$ and $\calY$, and families of output
	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
	$\{\pr{a,b}{x,y}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
\end{definition}
The size of a correlation is the sum of the sizes of the conditional probability distributions in the correlation.

@@

%---------------------------------------------------
\subsection{The game $\LS(r)$}
\label{sec:lsr_def}
%---------------------------------------------------
From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
we associate a variable $x(s)$ to each generator $s \in S$.
Then each linear relation in $R$ can be translated to a linear equation.
For example, the linear relation $f_0f_1f_2 = e$ is translated 
to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
$f_1g_1m_2 = J$ is translated to the equation
$x(f_1) + x(g_1) + x(m_2) = 1$. 
The complete list of the equations is given in \cref{def:lsg_eq}.
The construction of $\LS(r)$ proves the following theorem.
The definition of $\LS(r)$ follows this theorem.
\begin{theorem}
	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
\end{theorem}

\begin{definition}
\label{def:lsg}
The linear system game $\LS(r)$ consists of
\begin{align*}
    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
    & \calY^{\LS} = \{ x(s) : s \in S \},
\end{align*}
where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
and $\mr := 14r + 62$ is the number of equations.  
Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
Alice's answer sets are 
\begin{align*}
    \calA^{\LS}_{I_i} = (\Z_2)^{I_i}
\end{align*}
for $1 \leq i \leq \mr$.
Bob's answer set is
\begin{align*}
    \calB^{\LS} = \Z_2.
\end{align*}
The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
\begin{align*}
    \pi^{\LS}(I_i, x(s)) = 
    \begin{cases}
        1/N(r) & \text{ if } s \in I_i \\
        0 & \text{otherwise,}
    \end{cases}
\end{align*}
where $N(r) := 157r + 685$ is the total number of valid question pairs.
We define 
\begin{align*}
    X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \},
\end{align*}
which is the set of all the valid answers of equation $i$.
Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
the score function is
\begin{align*}
    V^{\LS}_{I_i, x(s)}(\ba, b) = 
    \begin{cases}
        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
        0 \text{, otherwise}.
    \end{cases}
\end{align*}
\end{definition}

As indicated above, the total
number of question pairs is $N(r) = 157r + 685 = \Theta(r)$.

@@

%====================================================
\section{Extending the weighted CHSH inequality $\I_\alpha$ into a nonlocal test}
\label{sec:ext_chsh}
%====================================================
In this section, we introduce the extended weighted CHSH test,
which is going to be a component of the full test introduced in \cref{sec:full_test}.
The ideal correlation for this test contains the ideal correlation that 
achieves $\I_{-\cot(\pi/d)}^{\max}$. 
To ease the study of the implication of a strategy that realize 
the ideal correlation of the extended weighted CHSH test,
we fill in the background of the robust self-testing property of the
general weighted CHSH inequality, $\I_\alpha$, first.

@@

% Intuitively, robust self-testing means that if some quantum strategy achieves a value $\I_\alpha$ that is close to $\I_\alpha^{\max}$,
% then the shared state must be close to $\ket{EPR}$ and their observables are close to the rotated Pauli operators 
% defined in \cref{def:ideal},
% up to some local isometry.
The formal statement is given in the theorem below. Since the proof uses the same techniques as in \cite{bamps2015},
we defer the proof till \cref{sec:w_chsh_proof}, and we only list the key relations that will be reused in \cref{sec:main} here.
\begin{theorem}
\label{thm:selftest}
    Define $\mu := \arctan(1/\alpha)$.
	If a quantum strategy $(\ket{\psi}, \{M_x:=M_x^0-M_x^1\}_{x=1,2}, \{N_y :=N_y^0-N_y^1\}_{y = 1,2} )$ achieves that
	$\I_\alpha \geq \I_\alpha^{\max} - \epsilon$
	for some $\epsilon > 0$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{junk}$  such that
	\begin{align*}
		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{junk} \x (\tM_x \x \tN_y) \ket{EPR}^{\x 2}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
		\frac{1}{\sin(\mu)^{3/2}})) \sqrt{\epsilon}
	\end{align*}
	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $\tM_x, \tN_y$ are 
	defined in \cref{def:ideal}.  
\end{theorem}
We follow the convention used in \cite{bamps2015},
which defines
\begin{align*}
	&Z_A := M_1 && X_A := M_2\\
	&Z_B := \frac{N_1+N_2}{2\cos{\mu}} && X_B := \frac{N_1-N_2}{2\sin{\mu}}.
\end{align*}
The key relations that will be reused are
\begin{align}
% 	\label{eq:za-zb}& Z_A\ket{\psi} \appd{O( \sqrt{\mu} \se)} Z_B\ket{\psi},\\
% 	\label{eq:xa-xb}&X_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B \ket{\psi}, \\
% 	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B(\1-Z_A) \ket{\psi},\\
% 	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} Z_B(\1-X_A) \ket{\psi},\\
% 	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} -X_AZ_A \ket{\psi},\\
% 	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{O(\frac{\se}{\mu^{3/2}})} -X_BZ_B \ket{\psi},
\label{eq:za-zb}& Z_A\ket{\psi} \appd{\frac{\sqrt{s\epsilon}}{c}} Z_B\ket{\psi},\\
	\label{eq:xa-xb}&X_A\ket{\psi} \appd{\frac{\sqrt{\epsilon}}{\sqrt{s}}} X_B \ket{\psi}, \\
	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{\frac{c+1}{c\sqrt{s}} \se} X_B(\1-Z_A) \ket{\psi},\\
	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{ \frac{s+1}{c\sqrt{s}} \se} Z_B(\1-X_A) \ket{\psi},\\
	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{\frac{1+c+s}{c\sqrt{s}} \se} -X_AZ_A \ket{\psi},\\
	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{\frac{2s^2+cs+c+s}{cs\sqrt{s}} \sqrt{\epsilon}} -X_BZ_B \ket{\psi}.
\end{align}
We keep the exact error terms for the substitution steps in \cref{sec:main}.
